%-------------------------
% Resume in Latex
% Author : Jared Coleman
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item[-]\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingTwo}[8]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
      \textit{\small#7} & \textit{\small #8} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://jaredraycoleman.com/}{\Large Jared Coleman}} & \href{mailto:jaredraycoleman@gmail.com}{jaredraycoleman@gmail.com}\\
  \href{https://jaredraycoleman.com/}{https://www.jaredraycoleman.com} \\
\end{tabular*}


% --------SKILLS------------
\section{Summary}
I have a broad interest in computer science.
My research interests include discrete mathematics, computational geometry, game theory, graph theory, distributed computing, automata theory, programming languages, formal methods, and mobile robotics.

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Southern California}{Long Beach, CA}
      {Ph.D. in Computer Science;  GPA: N/A}{Aug 2020 -- Present}
    \resumeSubheading
      {California State University, Long Beach}{Long Beach, CA}
      {Master of Science in Computer Science;  GPA: 4.00}{Aug 2018 -- May 2020}
    \resumeSubheading
      {California State University, Long Beach}{Long Beach, CA}
      {Bachelor of Science in Computer Science;  GPA: 3.6}{Aug 2013 -- May 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheadingTwo
      {The Aerospace Corporation}{El Segundo, CA}
      {Casual Member of the Technical Staff}{Aug 2020 -- Present}
      {Member of the Technical Staff}{Mar 2020 -- Aug 2020}
      {Associate Member of the Technical Staff}{Sep 2018 -- Mar 2020}
      \resumeItemListStart
        \item[-]{Develops algorithms for optimizing data-processing pipelines to maximize time and resource efficiency.}
        \item[-]{Helps build simulations for verifying flight software.}
        \item[-]{Designs software that helps Aerospace rapidly develop scalable, modular, and efficient analyses for launch vehicle verification in simulation, day-of-launch, and post-flight environments.}
      \resumeItemListEnd

    \resumeSubheading
      {The Aerospace Corporation}{El Segundo, CA}
      {Intern}{Jan 2018 -- Aug 2018}
      \resumeItemListStart
        \item[-]{Developed tools for automated data processing.}
        \item[-]{Worked on algorithms for cooperative mobile robotic systems.}
        \resumeItem{Skills Acquired}
            {Python, distributed algorithms, graph theory}
      \resumeItemListEnd

    \resumeSubheading
      {CSULB Research Foundation}{Long Beach, CA}
      {Student Research Assistant}{Mar 2017 -- May 2018}
      \resumeItemListStart
        \item[-]{Developed software for systems of cooperative robots.}
        \item[-]{Developed libraries for distributed robotic simulations.}
        \resumeItem{Skills Acquired}
          {Matlab, C/C++, distributed computing, data structures, algorithms, computer vision}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
    \resumeSubheading
    {Aerocube @ The Beach}{}
    {California State University, Long Beach}{}
    \resumeItemListStart
    \resumeItem{Supervisors}
        {Dr. Praveen Shankar (PI), Dr. Oscar Morales Ponce (Co-I)}
    \item[-]{Worked with an interdisciplinary team of student engineers to investigate the capabilities of the Nvidia Jetson TX1 as a computational unit in distributed robotics systems for space.}
    \item[-]{Developed localization, communication, path planning, and control algorithms.}
    \resumeItem{Skills Acquired}
        {C/C++, networking, distributed computing, teamwork, algorithms, software engineering}
    \resumeItemListEnd

    \resumeSubheading
    {Master's Thesis}{}
    {California State University, Long Beach}{}
    \resumeItemListStart
    \resumeItem{Committee Chair}{Dr. Oscar Morales Ponce}
    \resumeItem{Keywords}
        {pattern formation, computational geometry, mobile robotics}
    \item[-]{A study on optimal pattern formation. Given a set of robots and a target formation, our goal is to find optimal destinations such that the maximum distance any robot must travel is minimum.}
    \resumeItemListEnd
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
